---
title: "Shiny Application and Reproducible Pitch"
output: ioslides_presentation
date: "2023-01-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(gganimate)
```

## Project Goal

This peer assessed assignment has two parts.

First, you will create a Shiny application and deploy it on Rstudio’s servers.

Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Steps to Perform
- Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
- Deploy the application on Rstudio’s shiny server
- Share the application link by pasting it into the provided text box
- Share your server.R and ui.R code on github


## How to use the application
It is a simple application where you can choose iris characteristics.
The data used, and code are in github repository.





```{r, echo = TRUE}

```

## Slide with Plot

```{r}
ggplot(iris, aes(x = Petal.Length, y = Petal.Width)) +
  geom_point(
    aes(color = Species, shape = Species),
    size = 1.5, 
    alpha = 0.8 
  ) +
  # Use custom colors
  scale_color_manual(
    values = c("#386cb0", "#fdb462", "#7fc97f")
  )
```

